Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 paper.Rnw
changed the signature data code

# Create plot of the signatures
signatures %>%
  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(land~.) +
  ylim(c(-4,6)) +
  theme_bw(base_family = ff, base_size = f9_fs) +
  theme(strip.background = element_blank()) +
  ylab("Surface Measurement (in microns)") +
  xlab("Relative Location (in millimeters)")

@@

# Create or load the parallel coordinate plot
if (!file.exists("figure-10-1.png")) {

>>>>

# Create plot of the signatures
signatures %>%
  ggplot(aes(x = x/1000, y = sig)) + 
  geom_line() +
  facet_grid(land ~ .) +
  ylim(c(-4,6)) +
  theme_bw(base_family = ff, base_size = f9_fs) +
  theme(strip.background = element_blank()) +
  ylab("Surface Measurement (in microns)") +
  xlab("Relative Location (in millimeters)")

@@

# Create the parallel coordinate plot (if needed)
if (!file.exists("figure-10-1.png")) {
